Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2016-01-08 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
tweak panel ordering of advection contours and update discussion accordingly

Tracer contours at \(t = \SI{0}{\second}, \SI{5000}{\second}\) and \(\SI{10000}{\second}\) are shown in Figure~\ref{fig:advection-tracer}.
The most accurate results are found on the BTF grid using the upwind-biased cubic scheme (\ref{fig:advection-tracer}a).  As seen in figure~\ref{fig:advection-tracer}c, errors are less than \num{0.02} in magnitude and are confined to the expected region of the tracer.
At \(t = \SI{5000}{\second}\) the tracer is distorted by the terrain-following velocity field.  On the BTF grid, the tracer correctly returns to its original shape having cleared the mountain by \(t = \SI{10000}{\second}\), but this is not the case with centred linear scheme on the cut cell grid (figure~\ref{fig:advection-tracer}b).  Here, the tracer has spread vertically due to increased numerical errors when the tracer is transported between layers.
Dispersion errors are apparent with grid-scale oscillations that travel in the opposite direction to the wind (figure~\ref{fig:advection-tracer}d) and some artifacts remain above the mountain peak.

Similar accuracy is obtained for both centred linear and upwind-biased cubic schemes on the BTF grid (figures~\ref{fig:advection-tracer}c and~\ref{fig:advection-tracer}e).  However, results are substantially improved by using the upwind-biased cubic scheme on the cut cell grid (figures~\ref{fig:advection-tracer}d and~\ref{fig:advection-tracer}f).
Results on the SLEVE grid are comparable to those on the cut cell grid except that the artifacts above the mountain peak with the centred linear scheme on the cut cell grid are not present on the SLEVE grid (not shown).

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-advection-tracer/fig-advection-tracer.pdf}
%
	\caption{Tracer contours advected in a terrain following velocity field at \(t = \SI{0}{\second}\), \SI{5000}{\second} and \SI{10000}{\second} using (a) the upwind-biased cubic scheme on the BTF grid, and (b) the centred linear scheme on the cut cell grid with contour intervals every 0.1.  Errors at \(t = \SI{10000}{\second}\) are shown for (c) the the upwind-biased cubic scheme on the BTF grid, (d) the centred linear scheme on the cut cell grid, (e) the centred linear scheme on the BTF grid, and (f) the upwind-biased cubic scheme on the cut cell grid with contour intervals every 0.01.  Negative contours denoted by dotted lines.  The terrain profile is also shown immediately above the $x$ axis.}
	\label{fig:advection-tracer}
\end{figure*}

>>>>

Tracer contours at \(t = \SI{0}{\second}, \SI{5000}{\second}\) and \(\SI{10000}{\second}\) are shown in Figure~\ref{fig:advection-tracer} using the centred linear scheme on the BTF grid and cut cell grid (\ref{fig:advection-tracer}a and~\ref{fig:advection-tracer}b respectively).
At \(t = \SI{5000}{\second}\), the tracer is distorted by the terrain-following velocity field.  On the BTF grid, the tracer correctly returns to its original shape having cleared the mountain by \(t = \SI{10000}{\second}\), but this is not the case with centred linear scheme on the cut cell grid.  Here, the tracer has spread vertically due to increased numerical errors when the tracer is transported between layers.
Dispersion errors are apparent with grid-scale oscillations that travel in the opposite direction to the wind (figure~\ref{fig:advection-tracer}d) and some artifacts remain above the mountain peak.

A small improvement is obtained on the BTF grid by using the upwind-biased cubic scheme: as seen in figure~\ref{fig:advection-tracer}e, errors are less than \num{0.02} in magnitude and errors are confined to the expected region of the tracer.
However, results are substantially improved by using the upwind-biased cubic scheme on the cut cell grid (figure~\ref{fig:advection-tracer}f).
Results on the SLEVE grid are comparable to those on the cut cell grid except that the artifacts above the mountain peak with the centred linear scheme on the cut cell grid are not present on the SLEVE grid (not shown).

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-advection-tracer/fig-advection-tracer.pdf}
%
	\caption{Tracer contours advected in a terrain following velocity field at \(t = \SI{0}{\second}\), \SI{5000}{\second} and \SI{10000}{\second} using the centred linear scheme on (a) the BTF grid, and (b) the cut cell grid with contour intervals every 0.1.  Errors at \(t = \SI{10000}{\second}\) are shown for (c) the the centred linear scheme on the BTF grid, (d) the centred linear scheme on the cut cell grid, (e) the upwind-biased cubic scheme on the BTF grid, and (f) the upwind-biased cubic scheme on the cut cell grid with contour intervals every 0.01.  Negative contours denoted by dotted lines.  The terrain profile is also shown immediately above the $x$ axis.}
	\label{fig:advection-tracer}
\end{figure*}
